---
title: "短学期作业一"
author: "汪利军 3140105707"
date: "July 4, 2017"
fontsize: 12pt
output: 
  pdf_document:
    includes:
      in_header: ~/header_zh.tex
    latex_engine: xelatex
    number_sections: yes
    toc: yes
---

# 作业

## MB
Chapter 1: 2, 4, 6, 7, 8, 12, 18;

## MDL
Chapter 4 Exercise: 4.13, 4.14, 4.15, Chapter 3 Worksheet.

# MB
## Problem 1.2
orings 数据集在DAAG包中
```{r}
library(DAAG)
orings
```

Extract row 1, 2, 4, 11, 13 and 18 from orings

```{r}
orings.part = orings[c(1,2,4,11,13,18),]
```

Plot total incidents against temperature for the new data frame
```{r}
plot(orings.part$Temperature, orings.part$Total)
```
The similar plot for the full data set.
```{r}
plot(orings$Temperature, orings$Total)
```

## Problem 1.4
```{r}
library(DAAG)
str(ais)
```
判断缺失值
```{r}
which(is.na(ais))
```
也就是没有缺失值，所以每一列都无缺失值。
The table that shows the numbers of males and females for each different sport is as follows.
```{r}
table(ais$sex, ais$sport)
```
从上表可以看出，Gym，Netball，T_Sprnt和W_Polo存在large imbalance，前两项运动是女性居多，后两项运动是男性居多。


## Problem 1.6
构造数据集
```{r}
elevation = c(217, 254, 248, 254, 253, 227, 178, 207, 217)
area = c(24387, 5374, 4624, 2247, 1353, 1223, 1151, 755, 657)
my.Manitoba.lakes = data.frame(elevation, area)
row.names(my.Manitoba.lakes) = c("Winnipeg", "Winnipegosis", 
                                 "Manitoba", "SouthernIndian", 
                                 "Cedar", "Island", "Gods", 
                                 "Cross", "Playgreen")
rm(elevation)
rm(area)
```

### (a)
```{r}
attach(my.Manitoba.lakes)
plot(log2(area) ~ elevation, pch=16, xlim=c(170,280))
# NB: Doubling the area increases log2(area) by 1.0
text(log2(area) ~ elevation,
     labels=rownames(my.Manitoba.lakes), pos=4)
text(log2(area) ~ elevation, labels=area, pos=2)
title("Manitoba’s Largest Lakes")
detach(my.Manitoba.lakes)
```

### (b)
```{r}
attach(my.Manitoba.lakes)
plot(area ~ elevation, log = "y", pch = 16, xlim = c(170, 280))
text(area ~ elevation,
     labels=rownames(Manitoba.lakes), pos=4)
text(area ~ elevation, labels=area, pos=2)
title("Manitoba’s Largest Lakes")
detach(my.Manitoba.lakes)
```

## Problem 1.7
查看dotchart的帮助文档
```{r}
?dotchart
```

### (a)
```{r}
dotchart(Manitoba.lakes$area, 
         main = "Dotchart of Area (linear scale)", 
         labels = rownames(Manitoba.lakes))
```


### (b)
```{r}
dotchart(log2(Manitoba.lakes$area), 
         main = "Dotchart of Area (logarithmic scale)", 
         labels = rownames(Manitoba.lakes))
```

## Problem 1.8
The lower bound for the area of Manitoba covered by water is
```{r}
sum(Manitoba.lakes$area)
```

## Problem 1.12
```{r}
cutoff.prop <- function(x, cutoff)
{
  ## coerce list to vector
  if (is.list(x))
    x = as.numeric(unlist(x))
  n = length(x)
  ne = sum(x>cutoff)
  return(ne/n)
}
```

### (a)
```{r}
x = c(1:100)
## 超过90的比例
cutoff.prop(x, 90)
## 超过80的比例
cutoff.prop(x, 80)
```
### (b)

```{r}
library(Devore7)
dotplot(ex01.36)
```
数据集中未给出数据的单位，猜测为秒，则超过7分钟的比例为
```{r}
cutoff.prop(ex01.36, 60*7)
```


## Problem 1.18
```{r}
library(MASS)
## 原格式
Rabbit
```

```{r}
TA = unstack(Rabbit, Treatment~Animal)
TA
BA = unstack(Rabbit, BPchange~Animal)
BA
DA = unstack(Rabbit, Dose~Animal)
DA
```
因TA和DA对于五种Animal都相同，则取一列即可
```{r}
TA1 = TA[1]
DA1 = DA[1]
names(TA1) = "Treatment"
names(DA1) = "Dose"
```
然后进行cbind即可
```{r}
cbind(TA1, DA1, BA)
```

# MDL

## Problem 4.13
```{r}
seq(1.0, 2.0, by = 0.1)
```

## Problem 4.14
```{r}
rep(1:3, each = 2)
```

## Problem 4.15
```{r}
rep(1:3,2)
```

## Chapter 3 Worksheet
### 构造数据
```{r}
Gender <- factor(c("G", "G", "B", "G", "B", "B", "B", "B", "B", "B"))
ZEP <- c(T, T, T, T, F, T, F, T, T, T)
Weight <- c(16, 14, 13.5, 15.4, 16.5, 16, 17, 14.8, 17, 16.7)
Years <- c(3, 3, 3, 4, 3, 4, 3, 3, 4, 3)
Months <- c(5, 10, 5, 0, 8, 0, 11, 9, 1, 3)
Height <- c(100.0, 97.0, 95.5, 101.0, 100.0, 98.5, 103.0, 98.0, 101.5, 100.0)
df <- data.frame(Gender, ZEP, Weight, Years, Months, Height)
```
### 计算均值
```{r}
colMeans(df[c(3,4,5)])
```

### 计算BMI
```{r}
BMI = Weight/(Height*0.01)^2
BMI
```

