---
title: "R Notebook"
output: html_notebook
---

```{r}
library(DAAG)
```

# Statistical models

## Incorporation of an error or noise component

## Fitting models – the model formula

```{r}
## Fit line - by default, this fits intercept & slope.
## requires data frame roller (DAAG)
roller.lm <- lm(depression  ~  weight, data=roller)
## Compare with the code used to plot the data
plot(depression ~ weight, data=roller)
## Add the fitted line to the plot
abline(roller.lm)
```

# Distributions: models for the random component

```{r}
## To get labeled output exactly as below, see the footnote
dbinom(0:2, size=2, prob=0.5)
## determine such cumulative probabilities
pbinom(q = 1, size = 4, prob = 0.9)
qbinom(p = 0.70, size = 4, prob = 0.5)
```

```{r}
dpois(x = 0:4, lambda = 3)
ppois(q = 0:4, lambda = 3)
```

```{r}
## Plot the normal density, in the range -3 to 3
z <- pretty(c(-3,3), 30) # Find  ̃30 equally spaced points
ht <- dnorm(z)
# By default: mean=0, standard deviation=1
plot(z, ht, type="l",xlab="Normal deviate",ylab="Density",yaxs="i")
# yaxs="i" locates the axes at the limits of the data
```

# Simulation of random numbers and random samples
```{r}
set.seed(23286) # Use to reproduce the sample below
rbinom(10, size=1, p=.5)
```

## Simulation of regression data
```{r}
options(digits=3)
n <- 8; x <- seq(1,n); sigma <- 2.5; b0 <- 2; b1 <- 3
error <- rnorm(n, sd=sigma)
y <- b0 + b1*x + error
t(data.frame(x,y))
```

```{r}
roller.lm <- lm(depression  ~ weight, data=roller)
roller.sim <- simulate(roller.lm, nsim=20) # 20 simulations
with(roller, matplot(weight, roller.sim, pch=1, ylim=range(depression)))
points(roller, pch=16)
```

### Simulation of the sampling distribution of the mean
```{r}
## Function to generate n sample values; skew population
sampvals <- function(n) 
{
  exp(rnorm(n, mean = 0.5, sd = 0.3))
}
## Means across rows of a dimension nsamp x sampsize matrix of
## sample values gives nsamp means of samples of size sampsize.
samplingDist <- function(sampsize=3, nsamp=1000, FUN=mean)
{
  apply(matrix(sampvals(sampsize*nsamp), ncol=sampsize), 1, FUN)
}
size <- c(3,10,30)
## Simulate means of samples of 3, 9 and 30; place in dataframe
df <- data.frame(y3=samplingDist(sampsize=size[1]),
                 y9 = samplingDist(sampsize=size[2]),
                 y30 = samplingDist(sampsize=size[3]))
## Simulate source population (sampsize=1)
y <- samplingDist(sampsize=1)
densityplot(~y3+y9+y30, data = df, outer=TRUE, layout = c(3,1),
            plot.points = FALSE, panel = function(x, ...) {
              panel.densityplot(x, ..., col = "black")
              panel.densityplot(y, col = "gray40", lty = 2, ...)
              })
```


## Sampling from finite populations
```{r}
## For the sequence below, precede with set.seed(3676)
sample(1:9384, 15, replace=FALSE)
```

```{r}
split(sample(seq(1:10)), rep(c("Control","Treatment"), 5))
```

```{r}
sample(1:10, replace=TRUE)
```

# Model assumptions
```{r}
qreference(m=50, seed=21, nrep=5, nrows=1) # 50 values per panel
```

## Why models matter – adding across contingency tables
```{r}
str(UCBAdmissions)
## Tabulate by Admit and Gender
byGender <- margin.table(UCBAdmissions, margin=1:2)
round(100*prop.table(byGender, margin=2)["Admitted", ], 1)
## Admission rates, by department
round(100*prop.table(UCBAdmissions, margin=2:3)["Admitted", , ], 1)
```










